---
title: "Presentations"
output:
  distill::distill_article:
    toc: false
---

```{r panelset, layout='l-page', echo=FALSE}
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(foreground = "honeydew", background = "#0F2E3D")
```
Recent participation in conferences, seminars,  workshops,  interviews and the latest opinion pieces. 

::::: {.panelset}

::: {.panel}

#### Guest Speaker {.panel-name}

```{r setup, include=FALSE}

library(vembedr)

knitr::opts_chunk$set(echo = FALSE)
```

<li> **Disccusant**: *Conservadurismo Religioso y Política en el Perú: Una revisión histórica*, Conferencias Religión y Política, Diplomado en Religión y Política, Unidad de Pos Grado - UNMSM, February 22, 2022. </li>
```{r}
embed_url("https://www.youtube.com/watch?v=liU94Fc6taA") %>%
  use_align("center") %>% use_start_time("1h4m38s")
```

<li> **Interviewed**: *Perspectivas para analizar el rol de los partidos políticos*, POLITEAMA, December 27, 2021. </li>
```{r}
embed_url("https://www.youtube.com/watch?v=bgiNMujQ07s&t=1134s") %>%
  use_align("center")
```

<li> **Speaker**: *Los límites de entender la democracia como "democracia liberal"*, Sesión 3, Diálogos DEMOS, Universidad Nacional Mayor de San Marcos and Fundación Friedrich Ebert (FES) , October 2, 2021.</li>

```{r}
embed_url("https://www.youtube.com/watch?v=zZsSJEwRCcY") %>%
  use_align("center")  %>% use_start_time("1h33m45s")
```

:::

::: {.panel}

#### Workshops {.panel-name}

<li> **An Introduction to Electoral Studies**. Workshop on Electoral Systems and
Political Parties - Department of Political Science at National University of San Marcos, Lima, Peru, 24 and 31 July, 2021. *(online)*. \medskip </li>

<li>**Workshop on Research Methodology in Electoral Studies** Electoral
and of Governability School - National Court of Elections, Lima, Peru, 23 June - 5 July, *(online)*. \medskip </li>



:::

::: {.panel}

#### Opinion Pieces {.panel-name}

<li> [*¿Gobernar desde el Congreso?*](http://www.iepa.org.pe/gobernar-desde-el-congreso-i-gerson-julcarima-alvarez/), **Instituto de Estudios Políticos Andinos**, 14 de Febrero, 2021. \medskip </li>

```{r}
knitr::include_url("http://www.iepa.org.pe/gobernar-desde-el-congreso-i-gerson-julcarima-alvarez/")
```

<li> [*¿Crisis o sinceramiento de la representación política en el Perú?*](https://diariouno.pe/crisis-o-sinceramiento-de-la-representacion-politica-en-el-peru/), **Diario Uno**, 16 de Enero, 2020. \medskip </li>


```{r}
knitr::include_url("https://diariouno.pe/crisis-o-sinceramiento-de-la-representacion-politica-en-el-peru/")
```


<li> [*The Brazilian presidential election of 2018: Does a cartel of parties produce mavericks?*](https://presidential-power.net/?p=9608), **Presidential Power**, May 22th, 2019. \medskip </li>   

```{r}
knitr::include_url("https://presidential-power.net/?p=9608")
```

:::

:::::
